Negative Types

### 2015-04-04 Univalence/outline.tex
pi category

>>>>

Which still leaves open one big question: is our main representation
of permutations _fin~_ or CPerm ?  Or do we need both, as one is
'syntactic' (through the use of vectors) while the other is more
abstract (as it uses functions)?

I am quite sure that all the work needed to bring FinEquivCat all the
way to RigCategory is feasible, and not too hard [but will be
enlightening].

To do the same with CPermCat (and SkFinSetCategory) will be a fair bit
harder.  So it is very important for us to decide what the exact path
we want to take.  [Which is indeed what your outline is about!]
